---
title: "Formative_Assessment_markdown"
author: "CN 51034"
date: "2024-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Transformation

This is R Markdown document works with the data set airquality which contains airquality measurements in New York from may to September in 1973. Here we define a function called count_missing_values which, as the names says, counts missing values in each column in the dataset.

```{r}
# First we load the data set
data("airquality")

# We see the first 5 rows of the data
head(airquality)

# We define a function to help us count how many missing values we have in each column of the dataset

# Define a function to count missing values in each column
count_missing_values <- function(data) {
  transformed_data <- sapply(data, function(x) sum(is.na(x)))
  return(transformed_data)
}

# Finally we apply the function to the data set airquality
missing_values <- count_missing_values(airquality)
missing_values

```
The table below shows how many missing variables we have per variable. We can easiy see that the variable Ozone has 37 missing observations and Solar.R has 7 missing observations. The rest of the available variables do not have missing observations.

